Type-Safe Modular Parsing

### 2017-01-14 paper/sections/Inheritance.tex
Fix refs, spell check
Fix some refs

We already have solutions such Object Algebras~\cite{Oliveira2012} for this problem. However, when ASTs evolve, the corresponding parsers which produce such structures should also change accordingly. Our motivation is to build modular parsers, which can be extended together with ASTs. Futhermore, we focus on semantic modularity, that means we expect parsers to be modularly type-checked and separately compiled.

@@

\subsection{Multiple Extensions and Independent Extensibility}
A nice feature of Scala is its support for a form of multiple inheritance.
Scala has a linearized-style multiple inheritance for traits~\cite{}\huang{what's the proper citation here?}.
This can be very helpful when composing several languages, which
may have been independently developed. Suppose now
we want to compose the parsers for expressions from pre-defined
languages \inlinecode{LanguageA} and \inlinecode{LanguageB} using
alternative. The new parser can be built by inheriting both parsers
at the same time:

>>>>

We already have solutions such Object Algebras~\cite{Oliveira:2012} for this problem. However, when ASTs evolve, the corresponding parsers which produce such structures should also change accordingly. Our motivation is to build modular parsers, which can be extended together with ASTs. Futhermore, we focus on semantic modularity, that means we expect parsers to be modularly type-checked and separately compiled.

@@

\subsection{Multiple Extensions and Independent Extensibility}
A nice feature of Scala is its support for a form of multiple inheritance.
Scala has a linearized-style multiple inheritance for traits~\cite{odersky2004overview}. This can be very helpful when composing several languages, which
may have been independently developed. Suppose now
we want to compose the parsers for expressions from pre-defined
languages \inlinecode{LanguageA} and \inlinecode{LanguageB} using
alternative. The new parser can be built by inheriting both parsers
at the same time:

### 2017-01-14 paper/sections/RelatedWork.tex
Fix some refs

In OO languages, there are also many design patterns that achieve
type-safe extensibility~\cite{torgerson,odersky,Oliveira09,Oliveira:2012,Wang16}.\huang{not in the bib file, pls fix}
We chose Object Algebras~\cite{Oliveira:2012} because the pattern is
relatively lightweight and makes good use of existing OO features,
such as inheritance, generics and subtyping. As seen throughout the paper,
the parsing code is concise and expressive using Object Algebras.
In principle our approach is not coupled to the use of Object
Algebras, and variants of our approach could be used with other
extensibility techniques. Similarly to the work in functional
programming, the extensibility techniques in OOP have focused
on traversing and processing ASTs. We are unware of any work on OOP
that covers how to do modular parsing for extensible ASTs.

>>>>

In OO languages, there are also many design patterns that achieve
type-safe extensibility~\cite{torgersen2004expression,odersky2005independently,oliveira2009modular,Oliveira:2012,wang2016expression}. We chose Object Algebras~\cite{Oliveira:2012} because the pattern is
relatively lightweight and makes good use of existing OO features,
such as inheritance, generics and subtyping. As seen throughout the paper,
the parsing code is concise and expressive using Object Algebras.
In principle our approach is not coupled to the use of Object
Algebras, and variants of our approach could be used with other
extensibility techniques. Similarly to the work in functional
programming, the extensibility techniques in OOP have focused
on traversing and processing ASTs. We are unware of any work on OOP
that covers how to do modular parsing for extensible ASTs.
